---
title: "How to use this package"
author: "Mauricio Vargas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: ../inst/REFERENCES.bib
vignette: >
  %\VignetteIndexEntry{How to use this package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(eval = TRUE, message = FALSE, warning = FALSE)
```

# Basic trade example (Economy)

## Package data

I'll use this demo dataset to illustrate the essential usage of the functions
within this package.

```{r}
library(binet)

trade
```

## Balassa Index

You can obtain Balassa Index with `balassa_index()`.

```{r}
bi <- balassa_index(
  data = trade,
  source = "country",
  target = "product",
  value = "export_value"
)

bi
```

Another possibility is to obtain Balassa Index without discretization.

```{r}
bi_dec <- balassa_index(
  data =trade,
  source = "country",
  target = "product",
  value = "export_value",
  discrete = F
)

bi_dec
```

## Complexity Measures

You can compute complexity indexes (e.g. such as the Economic Complexity Index and Product Complexity Index) by using `complexity_measures()`. The calculations methods are *fitness* (default), *reflections*, *eigenvalues*. See [@measuringcomplexity2015] for the methodological details.

```{r}
com_fit <- complexity_measures(balassa_index = bi)

com_fit$complexity_index_source
com_fit$complexity_index_target
```

```{r}
com_ref <- complexity_measures(
  balassa_index = bi,
  method = "reflections"
)

com_ref$complexity_index_source
com_ref$complexity_index_target
```

```{r}
com_eig <- complexity_measures(
  balassa_index = bi,
  method = "eigenvalues"
)

com_eig$complexity_index_source
com_eig$complexity_index_target
```

## Proximity

Proximity matrices are used to create projections e.g. (country-country and product-product
networks) for bipartite networks. Using `proximity()` is straightforward.

```{r}
pro <- proximity(
  balassa_index = bi,
  balassa_sum_source = com_fit$balassa_sum_source,
  balassa_sum_target = com_fit$balassa_sum_target
)

pro$proximity_source
pro$proximity_target
```

## Networks

The `projections()` function is designed to use `igraph` for the internal
computations and also to pass proximity-based networks to `igraph`, `ggraph`
or export to Cytoscape by saving the output as csv/tsv.

```{r}
net <- projections(
  proximity_source = pro$proximity_source,
  proximity_target = pro$proximity_target,
  tolerance = 0.05
)

net$network_source
net$network_target
```

Just two basic examples with `ggraph`.

```{r, fig.width=20, fig.height=12}
library(igraph)
library(ggraph)
library(magrittr)

set.seed(200100)

net$network_source %>%
  graph_from_data_frame(directed = F) %>%
  ggraph(layout = "kk") +
  geom_edge_link(aes(edge_alpha = value, edge_width = value),
                 edge_colour = "#a8a8a8") +
  geom_node_point(color = "darkslategray4", size = 8) +
  geom_node_text(aes(label = name), vjust = 2.2) +
  ggtitle("The Country Space") +
  theme_void()
```

```{r, fig.width=20, fig.height=12}
net$network_target %>%
  graph_from_data_frame(directed = F) %>%
  ggraph(layout = "kk") +
  geom_edge_link(aes(edge_alpha = value, edge_width = value),
                 edge_colour = "#a8a8a8") +
  geom_node_point(color = "darkslategray4", size = 4) +
  geom_node_text(aes(label = name), vjust = 2.2) +
  ggtitle("The Product Space") +
  theme_void()
```

# References
