---
title: "How to use this package"
author: "Mauricio Vargas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: ../inst/REFERENCES.bib
vignette: >
  %\VignetteIndexEntry{How to use this package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(eval = TRUE, message = FALSE, warning = FALSE)
```

# Basic trade example (Economy)

## Package data

I'll use this demo dataset to illustrate the essential usage of the functions
within this package.

```{r}
library(binet)

trade_1962
```

## Balassa Index (or Revealed comparative Advantage, RCA)

You can obtain Balassa Index with `balassa_index()`.

```{r}
bi <- balassa_index(
  d = trade_1962,
  x = "country",
  y = "product",
  v = "value"
)

bi
```

You can also obtain it in matrix version.

```{r}
bi_m <- balassa_index(
  d = trade_1962,
  x = "country",
  y = "product",
  v = "value",
  tbl = F
)

# 5x5 preview
bi_m[1:5,1:5]
```

Another possibility is to obtain Balassa Index as a matrix or tibble without discretization.

```{r}
bi_dec <- balassa_index(
  d = trade_1962,
  x = "country",
  y = "product",
  v = "value",
  discrete = F
)

bi_dec
```

```{r}
bi_dec_m <- balassa_index(
  d = trade_1962,
  x = "country",
  y = "product",
  v = "value",
  tbl = F,
  discrete = F
)

# 5x5 preview
bi_dec_m[1:5,1:5]
```

## Complexity Measures

You can compute both Economic Complexity Index (ECI) and Product Complexity Index (PCI) by using `complexity_measures()`. The calculations methods are *reflections*, *eigenvalues* and *fitness* (default). See [@measuringcomplexity2015] for the methodological details.

```{r}
com_ref <- complexity_measures(
  bi = bi,
  x = "country",
  y = "product",
  v = "value",
  method = "reflections"
)

com_ref$complexity_index_x
com_ref$complexity_index_y
```

```{r}
com_eig <- complexity_measures(
  bi = bi,
  x = "country",
  y = "product",
  v = "value",
  method = "eigenvalues"
)

com_eig$complexity_index_x
com_eig$complexity_index_y
```

```{r}
com_fit <- complexity_measures(
  bi = bi,
  x = "country",
  y = "product",
  v = "value",
  method = "fitness"
)

com_fit$complexity_index_x
com_fit$complexity_index_y
```

## Proximity

Proximity matrices are used to create both country-country and product-product
networks. Using `proximity()` is straightforward.

```{r}
pro <- proximity(
  bi = bi,
  x = "country",
  y = "product",
  v = "value",
  d = com_fit$diversity,
  dx = "country",
  dv = "value",
  u = com_fit$ubiquity,
  uy = "product",
  uv = "value"
)

pro$proximity_x
pro$proximity_y
```

## Networks

The `proximity_networks()` function is designed to use `igraph` for the internal
computations and also to pass proximity-based networks to `igraph`, `ggraph`
or export to Cytoscape by saving the output as csv/tsv.

```{r}
net <- projections(
  px = pro$proximity_x,
  py = pro$proximity_y,
  tol = 0.1,
  f = "from",
  t = "to",
  v = "value"
)

net$network_x
net$network_y
```

Just two basic examples with `ggraph`.

```{r, fig.width=20, fig.height=12}
library(igraph)
library(ggraph)
library(magrittr)

set.seed(200100)

net$network_x %>%
  graph_from_data_frame(directed = F) %>%
  ggraph(layout = "kk") +
  geom_edge_link(aes(edge_alpha = value, edge_width = value),
                 edge_colour = "#a8a8a8") +
  geom_node_point(color = "darkslategray4", size = 8) +
  geom_node_text(aes(label = name), vjust = 2.2) +
  ggtitle("The Country Space") +
  theme_void()
```

```{r, fig.width=20, fig.height=12}
net$network_y %>%
  graph_from_data_frame(directed = F) %>%
  ggraph(layout = "kk") +
  geom_edge_link(aes(edge_alpha = value, edge_width = value),
                 edge_colour = "#a8a8a8") +
  geom_node_point(color = "darkslategray4", size = 4) +
  geom_node_text(aes(label = name), vjust = 2.2) +
  ggtitle("The Product Space") +
  theme_void()
```

# References
